Report and Figures

### 2016-11-11 figs.Rmd
multigroup maps

@@

summary <- compute_AUC(binary_loss_curves, adjust_thresh = 0.005) 
summary <- summary %>% left_join(cache, by = c('city' = 'city')) %>%
	left_join(info_summary[,c('city', 'J_XY', 'I_XY')]) %>%
	filter(I_XY > 0)

@@

@@

@@

>>>>

expand.grid(x = 1:8, y = 1:8) %>%
	mutate(`(a)` = .5,
		     `(b)` = (x > 4)*1,
		     `(c)` = ifelse(x == 7 & y %in% c(4,5), 0, `(b)`),
		     `(c)` = ifelse(x == 2 & y %in% c(4,5), 1, `(c)`),
		     `(d)` = (x + y) %% 2) %>%
	gather(key = model, value = p, -x, -y) %>%
	ggplot(aes(x = x, y = y)) +
	ggthemes::theme_map() +
  geom_tile(aes(fill = p)) +
	scale_fill_continuous(low = 'white', high = 'black ', limits=c(0,1)) +
	facet_grid(~model, switch = 'x') +
	xlab('') +
	ylab('') +
	guides(fill=FALSE) + 
	theme(axis.ticks = element_blank(),
		  axis.text.x = element_blank(),
		  axis.text.y = element_blank(),
		  panel.margin = unit(1, "mm"),
		  panel.background = element_rect(),
		  panel.grid.major = element_line(size = 0),
		  panel.grid.minor = element_line(size = 0),
		  strip.background = element_rect(fill = "white", color = "white", size = 2),
		  plot.margin=unit(c(1,1,0,0),"mm"),
		  strip.text=element_text(vjust=-100))

# g <- checkerboard_illustration() 
# g
# g + theme(text=element_text(size=10, family="Palatino"))
out_dir = 'figs/checkerboard_b.pdf'
ggsave(out_dir, width = 4, height = 1.3)
embed_fonts(out_dir, outfile=out_dir)
```

@@

summary <- compute_AUC(loss_curves, adjust_thresh = 0.005) 
summary <- summary %>% left_join(cache, by = c('city' = 'city')) %>%
	left_join(info_summary[,c('city', 'J_XY', 'I_XY')]) %>%
	filter(I_XY > 0)

@@

end_points <- data.frame(city = c('Atlanta', 'Philadelphia', 'Detroit'),
                         nclust = c(50, 7, 8),
                         I_XY = c(.36, .19, .44))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_text(aes(label = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.7), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

races <- c('Asian', 'Black', 'Hispanic', 'Other', 'White')
city <- 'Atlanta'

prominence_map <- function(city, races){
  tracts <- readOGR(dsn = paste0('data/cities/',city), layer = 'geo', verbose = FALSE)

  overall_dist <- tracts@data %>% 
  	select_(.dots = races) %>% 
  	colSums() %>% 
  	simplex_normalize()

  f <- function(row){
  here <- tracts@data[row,races] %>% 
  	simplex_normalize
  index <- which.max(here * log(here / overall_dist))
  return(races[index])
  }

  g <- function(row){
  	here <- tracts@data[row,races] %>% 
  		simplex_normalize
  	return(max(here * log(here / overall_dist), na.rm = T))
  }

  tracts@data$prominent_race <- 1:nrow(tracts@data) %>% 
  as.matrix() %>% 
  apply(FUN = f, MARGIN = 1)

  tracts@data$prominence <- 1:nrow(tracts@data) %>% 
  	as.matrix() %>% 
  	apply(FUN = g, MARGIN = 1)

  df <- tracts@data

  g <- tracts %>% fortify(region = 'GEOID') %>% 
      tbl_df() %>% 
      left_join(df, by = c('id' = 'GEOID')) %>% 
      ggplot() + 
      geom_polygon(aes(x = long, y = lat, fill = prominent_race, group = group, alpha = prominence))  +
      ggthemes::theme_map() + 
      scale_fill_brewer(palette = 'Set1') + 
      scale_alpha_continuous(guide = 'none', limits = c(0,1)) + 
      ggtitle(city) + 
      theme(text=element_text(size=16),
            plot.title = element_text(size=20, vjust = -5),
            legend.title = element_blank(),
            legend.position="bottom")
  g
}

cluster_map <- function(map, city_name, races, nclusters){

  tracts <- readOGR(dsn = paste0('data/cities/',city_name), layer = 'geo', verbose = FALSE)
  tracts <- tracts[sum(tracts@data[,races]) != 0,]
  clusters <- readRDS(paste0('throughput/clusterings/', city_name))
  loss_curves <- readr::read_csv('throughput/loss_curves.csv') %>%
  	group_by_('city') %>% 
  	arrange(desc(I_XY)) %>% 
  	mutate(I_XY = max(I_XY) - I_XY,
  		   nclust = row_number(),
  		   I_diff = I_XY - lag(I_XY))
    for(ncluster in nclusters){

  		weight <- loss_curves %>% filter(city == city_name, 
  					   nclust == ncluster) %>% 
  		ungroup() %>% 
  		select(I_diff) %>% 
  		as.numeric()

  		tracts@data$cluster <- cutree(clusters,ncluster)
  		overlay <- unionSpatialPolygons(tracts, IDs = tracts@data$cluster) %>% fortify()

  		g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 5*weight, color = 'black') 
    }

  max_weight <- loss_curves %>% filter(city == city_name) %>% 
  		ungroup() %>% 
  		summarise(max_diff = max(I_diff, na.rm = T)) %>% 
  		as.numeric()

  tracts@data$cluster <- 1
  overlay <- unionSpatialPolygons(tracts, IDs = tracts@data$cluster) %>% fortify()
  g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 5*max_weight, color = 'white')

  g
}

for(city in info_summary$city){
  print(city)

  g <- prominence_map(city, races)

  out_dir <- paste0('figs/batch_figs/prominence_map_', city, '.pdf')

  ggsave(out_dir, width = 14, height = 14, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)

  nclusters <- 1:6
  g <- g %>% cluster_map(city, races, nclusters)

  out_dir <- paste0('figs/batch_figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = 14, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}

city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)
g <- g %>% cluster_map(city, races, nclusters)

out_dir <- paste0('figs/prominence_map_Detroit.pdf')
ggsave(out_dir, width = 14, height = 14, units = 'cm')
embed_fonts(out_dir, outfile=out_dir)

labels <- data_frame(label = c('A', 'B', 'C', 'D', 'E', 'F'),
                     long   = c(-83.35, -83.1558, -83.164, -82.905, -83.055, -83.1258),
                     lat  = c(42.37, 42.39, 42.28, 42.4, 42.4, 42.3214))

g +
  geom_point(aes(x = long, y = lat), data = labels, size = 6, pch=21, color = 'black', fill = 'white', alpha = .6) + 
  geom_text(aes(x = long, y = lat, label = label), 
                  data = labels, 
                  size = 4, fontface = 'bold')

out_dir <- paste0('figs/cluster_map_Detroit.pdf')

ggsave(out_dir, width = 14, height = 14, units = 'cm')
embed_fonts(out_dir, outfile=out_dir)

```{r}
pal <- RColorBrewer::brewer.pal(name = 'Set1', 5)

make_cluster_groups('Detroit', 6) %>% 
	mutate(race = factor(race, levels = c('Asian', 'Other', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = race)) + 
  scale_fill_manual(values = c(pal[1], pal[4], pal[3], pal[2], pal[5]), name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8) + 
  scale_alpha_continuous(guide = 'none', limits = c(0, 1)) + 
	theme_minimal() + 
	theme(
	  text=element_text(size=25),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())
